Library Parser

### 2024-06-04 studies/library_parser.qmd
update library parser

```{r}
# create new column containing information between two adjacent target fields for all entries in list
meta_df <- lapply(meta_list, function(x) str_match(toString(x), field_names))
# collapse list entries into rows
meta_df <- do.call('rbind', meta_df)
# format as a data.frame
meta_df <- data.frame(meta_df)
# match text after final column name
meta_df[,ncol(meta_df)+1] <- sapply(meta_df[,1], function(x) str_match(toString(x), '(?<=MODEL_VALIDATION).*'))
# replace first column with citationkeys
meta_df[,1] <- names(meta_list)
names(meta_df) <- c('citekey', search_fields)
```

@@

```{r}
## remove bibtext field formatting
# remove curly braces
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\{')) 
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\}'))
# remove first '=' (from bibtex field )
meta_df <- apply(meta_df, 2, function(x) str_remove(x, '='))
# remove double-commas
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ',,'))
# remove comments
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '%%.*'))
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ' , '))
meta_df <- as.data.frame(meta_df)
```

```{r}
knitr::kable(meta_df)
```

>>>>

```{r}
# create new column containing information between two adjacent target fields for all entries in list
meta_df <- lapply(meta_list, function(x) str_match(paste0(x, collapse = ' '), field_names))
meta_df <- lapply(meta_list, function(x) str_match(paste0(x, collapse = ' '), field_names))

# collapse list entries into rows
meta_df <- do.call('rbind', meta_df)
# format as a data.frame
meta_df <- data.frame(meta_df)
# match text after final column name
meta_df[,ncol(meta_df)+1] <- sapply(meta_df[,1], function(x) str_match(paste0(x, collapse = ' '), '(?<=MODEL_VALIDATION).*'))
# replace first column with citationkeys
meta_df[,1] <- names(meta_list)
names(meta_df) <- c('citekey', search_fields)
```

@@

```{r}
## remove bibtext field formatting
# remove curly braces
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\{')) 
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\},'))
# remove first '=' (from bibtex field )
meta_df <- apply(meta_df, 2, function(x) str_remove(x, '='))
# remove double-commas
#meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ',,'))
# remove comments
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '%%.*'))
#meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ' , '))
meta_df <- as.data.frame(meta_df)
```

```{r}
knitr::kable(meta_df)
```
Evaluate cell as r code example
```{r}
eval(parse(text = meta_df$model_rate_emotion_values[12]))
```
